*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-05-19 inst/manuscript/manuscript.rmd
Switch to "WCM-Q";

†
:    \
    Research Division, Weill Cornell Medical College in Qatar, P.O.Box 24144, Doha, State of Qatar

@@

# Funding
J.G., R.J.C. and the Proteomics Core at WCMC-Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medical College in Qatar, a program 
funded by Qatar Foundation. This study was made possible by NPRP grant
5-669-1-112 from the Qatar National Research Fund (a member of Qatar 
Foundation).The statements made herein are solely the responsibility of the
authors. B.P. was also supported by the Austrian Science Fund (FWF), project
J3686-B21.

>>>>

†
:    \
    Research Division, Weill Cornell Medicine -- Qatar, P.O.Box 24144, Doha, State of Qatar

@@

# Funding
J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medicine -- Qatar, a program 
funded by Qatar Foundation. This study was made possible by NPRP grant
5-669-1-112 from the Qatar National Research Fund (a member of Qatar 
Foundation).The statements made herein are solely the responsibility of the
authors. B.P. was also supported by the Austrian Science Fund (FWF), project
J3686-B21.
